\section{Data}
\subsection{Overview}
The study used 16 right-handed, healthy, English-speaking participants 
recruited through ads posted on UCLA. Out of 16 subjects, 9 were female and 
the mean age was 22 $ \pm $ 2.9 years. \cite{Tom2007LossAversion}

\subsection{Behavorial Data}
The behavioral data consists of each subject undergoing 3 trial runs for the 
``gamble'' task, in which each subject is presented with a combination of 
potential monetary gains and losses given a 50/50 chance of to win/loss. Each 
trial run consists of 86 different combinations of rewards/penalities spread 
out accross 474 seconds. Intervals between each onset of task range from 4 to 
8 seconds. Subjects were given the 4 choices in reponse to each gambling 
proposal:
\begin{enumerate}
  \item Strong Accept
  \item Weak Accept
  \item Weak Reject
  \item Strong Reject
\end{enumerate}
The choices are recorded by denoting reponse numbers 1, 2, 3, and 4, 
respectively. Furthermore, the response time for each gambling decision was 
recorded in seconds. 
\subsection{BOLD Data}
Blood-oxygen-level dependent (BOLD) imaging data were collected from each 
subject as he/she performed the gamble tasks. 240 time scans were done on each 
run with a time between each scan of 2 seconds. So total scanning time is 480 
seconds. Each scan consists of a snapshot consisting of a64 by 64 by 34 image 
matrix. 

There are also 4 model conditions, with events corresponding to 
\begin{enumerate}
  \item Task
  \item Parametric Gain
  \item Parametric Loss
  \item Distance from Indifference
\end{enumerate}